parental migration and adolescents educational performance

### 2022-06-29 data/Gu-thesis-script.Rmd
version before presentation

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
library(MatchIt)
#library(vtable)
library(ggplot2)
library(labelled)
library(cobalt) 
#library(gtsummary)
#library(DescTools)
#knitr::opts_chunk$set(modelsummary_get="broom")
```

@@

Remove wave 1's observations of grade 9; they were not followed up in wave 2
```{r}
d_stu1 <- d_stu1 %>% 
  subset(grade9==0) %>% 
  select(!c(frame, subsample, sweight, grade9))
d_stu2 <- d_stu2 %>% 
  select(!c(w2frame, w2subsample, w2sweight, w1w2sweight))
d_par1 <- d_par1 %>% 
  subset(grade9==0) %>% 
  select(!c(frame, subsample, grade9))
```

Assemble a panel dataset in wide format
```{r}
dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) 
dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids')) %>% remove_labels()
```

```{r}
d <- d %>% mutate(
  child.age = 2013 - a02a, #student's age at baseline
  w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
  w1mat_100 = tr_mat/w2upmat*100,
  w1eng_100 = tr_eng/w2upeng*100,
  w2chn_100 = w2chn/w2upchn*100,
  w2mat_100 = w2mat/w2upmat*100,
  w2eng_100 = w2eng/w2upeng*100
)
```

Trimming outliers
```{r}
d <- d %>% mutate(
  w1chn_100_trim = if_else(w1chn_100>100, 100, w1chn_100),
  w2chn_100_trim = if_else(w2chn_100>100, 100, w2chn_100),
  w1mat_100_trim = if_else(w1mat_100>100, 100, w1mat_100),
  w2mat_100_trim = if_else(w2mat_100>100, 100, w2mat_100),
  w1eng_100_trim = if_else(w1eng_100>100, 100, w1eng_100),
  w2eng_100_trim = if_else(w2eng_100>100, 100, w2eng_100)
)
```

```{r}
d <- d %>% mutate(
  w1ttl_100 = w1chn_100_trim + w1mat_100_trim + w1eng_100_trim,
  w2ttl_100 = w2chn_100_trim + w2mat_100_trim + w2eng_100_trim,
  ttl_dif = w2ttl_100 - w1ttl_100,
  cog_dif = w2cog3pl - cog3pl
  )
```

```{r}
d1 <- d %>%
  drop_na(cog_dif, ttl_dif, child.age)
```

within-class z score
```{}
d1 <- d1 %>% group_by(clsids + w2clsids) %>%
  mutate(
    w1ttl_z = as.numeric(scale(w1ttl)),
    w2ttl_z = as.numeric(scale(w2ttl))
  ) %>% ungroup()
```

```{}
d1 <- d1 %>% group_by(clsids + w2clsids) %>%
  mutate(
    w1ttl_std = rescale(w1ttl),
    w2ttl_std = rescale(w2ttl)
    ) %>% ungroup()
```

Detect outliers
```{}
d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
d_outlier1 <- d_outlier %>% select(clsids, clsids + w2clsids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
d1 <- d %>% anti_join(d_outlier, by=c('ids', 'clsids', 'clsids + w2clsids', 'ctyids'))
```

Sample
```{r}
d_cl <- d1 %>% 
  filter(w2a0801==1) %>% #keep parents who are married (and alive)
  filter(be1201==1 & be1202==1) %>% #keep both parents live with children at baseline
  filter(stmigrant==1) #keep local children 
```

@@

Control variables
```{r}
d_cl <- d_cl %>% mutate(
         child.is.girl = if_else(a01 == 2, 1, 0), #student is girl
         child.has.rural.hukou = sthktype, #student holds rural (agricultural) hukou
         child.in.boarding.school = stbrd, #student is boarding at school
         child.is.ethnic.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
         child.health.self.rated = a17, #student's self-rated health
         child.had.skipped.grade = if_else(c03 == 0, 0, 1), #student had skipped grade
         child.had.repeated.grade = if_else(c04 == 0, 0, 1), #student had repeated grade
         #ch.illness = if_else(a10 == 1, 1, 0), #student had serious illness before primary school
         child.went.to.preschool = if_else(c01 == 1, 1, 0), #student had attended preschool
         #ch.par.rltn = if_else(stprrel == 2, 1, 0),
         #ch.tutoring = if_else(b1901 == 1|b1902 == 1|b1903 == 1|b1904 == 1, 1, 0),
         par.edu = stprhedu, #Among two parents, the best-educated one's educational level
         parent.has.white.collar.job = if_else(be08==1|be08==2|be08==3, 1, 0),
         #par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
         home.economic.resource = steco_5c, #self-rated household financial situation
         home.has.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
         home.extracurricular.book = b12 #Amount of book at home, student self-rated 
) %>% drop_na(
child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, par.edu, 
#par.ccp, 
parent.has.white.collar.job, home.has.internet, home.extracurricular.book, home.economic.resource)
```

```{r}
d_cl$stsib <- d_cl$stsib %>% replace_na(0) %>% as.numeric()
d_cl <- d_cl %>% mutate(child.number.of.sibling = if_else(stonly == 1, 0, stsib)) %>% #number of siblings
  drop_na(child.number.of.sibling)
```

Best-educated parent's years of education
```{}
d_cl <- d_cl %>% mutate(parent.educational.level = NA)
d_cl$parent.educational.level[d_cl$par.edu == 1] <- 0
d_cl$parent.educational.level[d_cl$par.edu == 2] <- 6
d_cl$parent.educational.level[d_cl$par.edu == 3] <- 9
d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
d_cl$parent.educational.level[d_cl$par.edu == 7] <- 15
d_cl$parent.educational.level[d_cl$par.edu == 8] <- 16
d_cl$parent.educational.level[d_cl$par.edu == 9] <- 19
```

```{r}
d_cl <- d_cl %>% mutate(parent.educational.level = NA)
d_cl$parent.educational.level[d_cl$par.edu == 1|d_cl$par.edu == 2] <- 1
d_cl$parent.educational.level[d_cl$par.edu == 3] <- 2
d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 3
d_cl$parent.educational.level[d_cl$par.edu == 7] <- 4
d_cl$parent.educational.level[d_cl$par.edu == 8] <- 5
d_cl$parent.educational.level[d_cl$par.edu == 9] <- 6
```

```{r}
d_cl <- d_cl %>% mutate(parent.expectation.on.child = NA)
d_cl$parent.expectation.on.child[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
d_cl$parent.expectation.on.child[d_cl$ba18 == 3|d_cl$ba18 == 4|d_cl$ba18 == 5] <- 2
d_cl$parent.expectation.on.child[d_cl$ba18 == 6] <- 3
d_cl$parent.expectation.on.child[d_cl$ba18 == 7] <- 4
d_cl$parent.expectation.on.child[d_cl$ba18 == 8|d_cl$ba18 == 9] <- 5
```

```{r}
d_cl <- d_cl %>% mutate(child.educational.aspiration = NA)
d_cl$child.educational.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
d_cl$child.educational.aspiration[d_cl$c22 == 3|d_cl$c22 == 4|d_cl$c22 == 5] <- 2
d_cl$child.educational.aspiration[d_cl$c22 == 6] <- 3
d_cl$child.educational.aspiration[d_cl$c22 == 7] <- 4
d_cl$child.educational.aspiration[d_cl$c22 == 8|d_cl$c22 == 9] <- 5
```

```{r}
d_cl <- d_cl %>%  drop_na(
  parent.educational.level, 
  parent.expectation.on.child, 
  child.educational.aspiration)
```

## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r}
d_cl <- d_cl %>% mutate(
  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
  migr_fa_only = NA,
  #migr_fa = NA,
  migr_mo_only = NA,
  #migr_mo = NA,
  migr_both = NA
  ) %>% drop_na(migr)
```

@@

```{}
df <- d_cl %>% select(
  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
  cog3pl, w1ttl_100, cog_dif, ttl_dif,
  child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.educational.aspiration, 
  par.edu, par.ccp, par.expt.univ, 
  home.has.internet, home.extracurricular.book, home.economic.resource
)
```

## Descriptive statistics
```{r}
d_migr <- d_cl %>%
  select(
  migr, migr_mo_only, migr_fa_only, migr_both,
  cog3pl, w2cog3pl, w1ttl_100, w2ttl_100, cog_dif, ttl_dif,
  child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
  child.health.self.rated, child.educational.aspiration, 
  parent.educational.level, parent.expectation.on.child, 
  home.extracurricular.book, home.economic.resource) 
```

```{r}
d_smr <- d_migr %>% 
  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) %>% 
  mutate(`Parental Migration Type` = 0) 
d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother Migrated'
d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father Migrated'
d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents Migrated'
d_smr <- d_smr %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

@@

```{r}
d_dpvar <- d_migr %>%
  select(#migr, 
         cog_dif, cog3pl, w2cog3pl, ttl_dif, w1ttl_100, w2ttl_100) %>%
  rename(
    `Cognitive score at wave 1` = cog3pl,
    `Cognitive score at wave 2` = w2cog3pl,
    `Academic exam score at wave 1` = w1ttl_100,
    `Academic exam score at wave 2` = w2ttl_100,
    `Cognitive score difference` = cog_dif,
    `Academic exam score difference` = ttl_dif
  ) 
```

```{}
d_dpvar %>%
  tbl_summary(
    by = migr,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = all_continuous() ~ 2,
    ) %>% add_p() %>% as_kable()
```

```{r}
#table_independent_variable <- 
  st(
  d_dpvar,
  digits = 2, 
  group = 'migr',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = 'kable')
#table_independent_variable 
```

```{r}
d_dpvar <- as.data.frame(d_dpvar)
table_dependent_variable <- datasummary(
  All(d_dpvar) ~ Mean + SD + Min + Max,
  data = d_dpvar,
  output = 'markdown'
  )
table_dependent_variable
```

```{r}
d_idpvar <- d_migr %>% 
  select(migr, migr_mo_only, migr_fa_only, migr_both) %>% 
  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) %>% 
  mutate(`Parental Migration Type` = 0) 
d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents At Home'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother Migrated'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father Migrated'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
d_idpvar <- d_idpvar %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

@@

```{r}
d_ctvar <- d_migr %>%
  select(migr, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
  child.health.self.rated, child.educational.aspiration, 
  parent.educational.level, parent.expectation.on.child, 
  home.extracurricular.book, home.economic.resource) %>% 
  mutate_if(is.numeric, as.factor)
```

```{r}
d_ctvar$parent.educational.level <- d_ctvar$parent.educational.level %>% 
  recode_factor(
    '1' = 'Primary school and below',
    '2' = 'Junior high school',
    '3' = 'Senior high school',
    '4' = 'Associate college',
    '5' = 'University',
    '6' = 'Postgraduate'
  )
d_ctvar$child.educational.aspiration <- d_ctvar$child.educational.aspiration %>%
  recode_factor(
    '1' = 'Junior high school',
    '2' = 'Senior high school',
    '3' = 'Associate college',
    '4' = 'University',
    '5' = 'Postgraduate'     
  )
d_ctvar$parent.expectation.on.child  <- d_ctvar$parent.expectation.on.child %>%
  recode_factor(
    '1' = 'Junior high school',
    '2' = 'Senior high school',
    '3' = 'Associate college',
    '4' = 'University',
    '5' = 'Postgraduate'    
  )
d_ctvar$home.economic.resource <- d_ctvar$home.economic.resource %>% 
  recode_factor(
    '1' = 'Very poor',
    '2' = 'Somewhat poor',
    '3' = 'Moderate',
    '4' = 'Somewhat rich',
    '5' = 'Very rich'
  )
d_ctvar$child.health.self.rated <- d_ctvar$child.health.self.rated %>%
  recode_factor(
    '1' = 'Very poor',
    '2' = 'Not very good',
    '3' = 'Moderate',
    '4' = 'Good',
    '5' = 'Very good'
  )
d_ctvar$home.extracurricular.book <- d_ctvar$home.extracurricular.book %>%
  recode_factor(
    '1' = 'Very few',
    '2' = 'Not many',
    '3' = 'Some',
    '4' = 'Quite a few',
    '5' = 'A great number'
  )
```

```{}
test.table <- d_ctvar %>%
  tbl_summary(
    by = migr,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    ) 
```

```{r}
test_table <- datasummary_balance(
  ~migr,
  data = d_ctvar
)
test_table
```

```{}
#table_control_variable <- 
table_balance <- st(
  d_ctvar,
  digits = 2, 
  group = 'migr',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = "return")
#table_control_variable 
```

```{r}
table_control_variable <- datasummary_skim(
  data = d_ctvar,
  type = 'categorical',
  output = 'markdown'
)
table_control_variable
```

```{r}
d_migr <- d_migr %>% mutate(`Parental Migration` = ifelse(migr == 1, 'Yes', 'No'))
d_migr <- d_migr %>% mutate(`Parental Migration Type` = 0) 
d_migr$`Parental Migration Type`[d_migr$migr==0] <- 'Both Parents At Home'
d_migr$`Parental Migration Type`[d_migr$migr_mo_only==1] <- 'Only Mother Migrated'
d_migr$`Parental Migration Type`[d_migr$migr_fa_only==1] <- 'Only Father Migrated'
d_migr$`Parental Migration Type`[d_migr$migr_both==1] <- 'Both Parents Migrated'
d_migr <- d_migr %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

Whole sample summary
```{}
table_sum <- st(
  d_migr,
  digits = 2, 
  out = 'kable')
table_sum
```

```{}
table_sum_migr <- st(
  d_migr,
  group = 'Parental Migration', 
  digits = 2, 
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = 'kable')
table_sum_migr
```

@@

```{r}
set.seed(1)
fig_cog <- 
  ggplot(d_migr, aes(x=`Parental Migration`, y=cog_dif, fill = `Parental Migration`)) + 
    geom_violin()+
    xlab('Parental Migration') +
    theme(legend.position="none") +
    ylab("")
fig_cog
```

```{r}
set.seed(1)
fig_ttl <- 
  ggplot(d_migr, aes(x=`Parental Migration`, y=ttl_dif, fill = `Parental Migration`)) + 
    geom_violin()+
    xlab('Parental Migration') +
    theme(legend.position="none") +
    ylab("")
fig_ttl
```

>>>>

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
library(MatchIt)
library(vtable)
library(ggplot2)
library(labelled)
library(cobalt) 
#library(gtsummary)
#library(DescTools)
#knitr::opts_chunk$set(modelsummary_get="broom")
```

@@

Remove wave 1's observations of grade 9; they were not followed up in wave 2
```{r}
d_stu1 <- d_stu1 |> 
  subset(grade9==0) |> 
  select(!c(frame, subsample, sweight, grade9))
d_stu2 <- d_stu2 |> 
  select(!c(w2frame, w2subsample, w2sweight, w1w2sweight))
d_par1 <- d_par1 |> 
  subset(grade9==0) |> 
  select(!c(frame, subsample, grade9))
```

Assemble a panel dataset in wide format
```{r}
dw1 <- d_stu1 |> left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) 
dw2 <- d_stu2 |> left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- dw1 |> right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids')) |> remove_labels()
```

```{r}
d <- d |> mutate(
  child.age = 2013 - a02a, #student's age at baseline
  w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
  w1mat_100 = tr_mat/w2upmat*100,
  w1eng_100 = tr_eng/w2upeng*100,
  w2chn_100 = w2chn/w2upchn*100,
  w2mat_100 = w2mat/w2upmat*100,
  w2eng_100 = w2eng/w2upeng*100
)
```

Trimming outliers
```{r}
d <- d |> mutate(
  w1chn_100_trim = if_else(w1chn_100>100, 100, w1chn_100),
  w2chn_100_trim = if_else(w2chn_100>100, 100, w2chn_100),
  w1mat_100_trim = if_else(w1mat_100>100, 100, w1mat_100),
  w2mat_100_trim = if_else(w2mat_100>100, 100, w2mat_100),
  w1eng_100_trim = if_else(w1eng_100>100, 100, w1eng_100),
  w2eng_100_trim = if_else(w2eng_100>100, 100, w2eng_100)
)
```

```{r}
d <- d |> mutate(
  w1ttl_100 = w1chn_100_trim + w1mat_100_trim + w1eng_100_trim,
  w2ttl_100 = w2chn_100_trim + w2mat_100_trim + w2eng_100_trim,
  ttl_dif = w2ttl_100 - w1ttl_100,
  cog_dif = w2cog3pl - cog3pl
  )
```

```{r}
d1 <- d |>
  drop_na(cog_dif, ttl_dif, child.age)
```

within-class z score
```{}
d1 <- d1 |> group_by(clsids + w2clsids) |>
  mutate(
    w1ttl_z = as.numeric(scale(w1ttl)),
    w2ttl_z = as.numeric(scale(w2ttl))
  ) |> ungroup()
```

```{}
d1 <- d1 |> group_by(clsids + w2clsids) |>
  mutate(
    w1ttl_std = rescale(w1ttl),
    w2ttl_std = rescale(w2ttl)
    ) |> ungroup()
```

Detect outliers
```{}
d_outlier <- d |> filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
d_outlier1 <- d_outlier |> select(clsids, clsids + w2clsids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
d1 <- d |> anti_join(d_outlier, by=c('ids', 'clsids', 'clsids + w2clsids', 'ctyids'))
```

Sample
```{r}
d_cl <- d1 |> 
  filter(w2a0801==1) |> #keep parents who are married (and alive)
  filter(be1201==1 & be1202==1) |> #keep both parents live with children at baseline
  filter(stmigrant==1) #keep local children 
```

@@

Control variables
```{r}
d_cl <- d_cl |> mutate(
         child.is.girl = if_else(a01 == 2, 1, 0), #student is girl
         child.has.rural.hukou = sthktype, #student holds rural (agricultural) hukou
         child.in.boarding.school = stbrd, #student is boarding at school
         child.is.ethnic.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
         child.health.self.rated = a17, #student's self-rated health
         child.had.skipped.grade = if_else(c03 == 0, 0, 1), #student had skipped grade
         child.had.repeated.grade = if_else(c04 == 0, 0, 1), #student had repeated grade
         #ch.illness = if_else(a10 == 1, 1, 0), #student had serious illness before primary school
         child.went.to.preschool = if_else(c01 == 1, 1, 0), #student had attended preschool
         #ch.par.rltn = if_else(stprrel == 2, 1, 0),
         #ch.tutoring = if_else(b1901 == 1|b1902 == 1|b1903 == 1|b1904 == 1, 1, 0),
         par.edu = stprhedu, #Among two parents, the best-educated one's educational level
         parent.has.white.collar.job = if_else(be08==1|be08==2|be08==3, 1, 0),
         #par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
         home.economic.resource = steco_5c, #self-rated household financial situation
         home.has.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
         home.extracurricular.book = b12 #Amount of book at home, student self-rated 
) |> drop_na(
child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, par.edu, 
#par.ccp, 
parent.has.white.collar.job, home.has.internet, home.extracurricular.book, home.economic.resource)
```

```{r}
d_cl$stsib <- d_cl$stsib |> replace_na(0) |> as.numeric()
d_cl <- d_cl |> mutate(child.number.of.sibling = if_else(stonly == 1, 0, stsib)) |> #number of siblings
  drop_na(child.number.of.sibling)
```

Best-educated parent's years of education
```{}
d_cl <- d_cl |> mutate(parent.educational.level = NA)
d_cl$parent.educational.level[d_cl$par.edu == 1] <- 0
d_cl$parent.educational.level[d_cl$par.edu == 2] <- 6
d_cl$parent.educational.level[d_cl$par.edu == 3] <- 9
d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
d_cl$parent.educational.level[d_cl$par.edu == 7] <- 15
d_cl$parent.educational.level[d_cl$par.edu == 8] <- 16
d_cl$parent.educational.level[d_cl$par.edu == 9] <- 19
```

```{r}
d_cl <- d_cl |> mutate(parent.educational.level = NA)
d_cl$parent.educational.level[d_cl$par.edu == 1|d_cl$par.edu == 2] <- 1
d_cl$parent.educational.level[d_cl$par.edu == 3] <- 2
d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 3
d_cl$parent.educational.level[d_cl$par.edu == 7] <- 4
d_cl$parent.educational.level[d_cl$par.edu == 8] <- 5
d_cl$parent.educational.level[d_cl$par.edu == 9] <- 6
```

```{r}
d_cl <- d_cl |> mutate(parent.expectation.on.child = NA)
d_cl$parent.expectation.on.child[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
d_cl$parent.expectation.on.child[d_cl$ba18 == 3|d_cl$ba18 == 4|d_cl$ba18 == 5] <- 2
d_cl$parent.expectation.on.child[d_cl$ba18 == 6] <- 3
d_cl$parent.expectation.on.child[d_cl$ba18 == 7] <- 4
d_cl$parent.expectation.on.child[d_cl$ba18 == 8|d_cl$ba18 == 9] <- 5
```

```{r}
d_cl <- d_cl |> mutate(child.educational.aspiration = NA)
d_cl$child.educational.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
d_cl$child.educational.aspiration[d_cl$c22 == 3|d_cl$c22 == 4|d_cl$c22 == 5] <- 2
d_cl$child.educational.aspiration[d_cl$c22 == 6] <- 3
d_cl$child.educational.aspiration[d_cl$c22 == 7] <- 4
d_cl$child.educational.aspiration[d_cl$c22 == 8|d_cl$c22 == 9] <- 5
```

```{r}
d_cl <- d_cl |>  drop_na(
  parent.educational.level, 
  parent.expectation.on.child, 
  child.educational.aspiration)
```

## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r}
d_cl <- d_cl |> mutate(
  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became Migrated from household between baseline and endline survey
  migr_fa_only = NA,
  #migr_fa = NA,
  migr_mo_only = NA,
  #migr_mo = NA,
  migr_both = NA
  ) |> drop_na(migr)
```

@@

```{}
df <- d_cl |> select(
  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
  cog3pl, w1ttl_100, cog_dif, ttl_dif,
  child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.educational.aspiration, 
  par.edu, par.ccp, par.expt.univ, 
  home.has.internet, home.extracurricular.book, home.economic.resource
)
```

## Descriptive statistics
```{r}
d_migr <- d_cl |>
  select(
  migr, migr_mo_only, migr_fa_only, migr_both,
  cog3pl, w2cog3pl, w1ttl_100, w2ttl_100, cog_dif, ttl_dif,
  child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
  child.health.self.rated, child.educational.aspiration, 
  parent.educational.level, parent.expectation.on.child, 
  home.extracurricular.book, home.economic.resource) 
```

```{r}
d_smr <- d_migr |> 
  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) |> 
  mutate(`Parental Migration Type` = 0) 
d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother Migrated'
d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father Migrated'
d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents Migrated'
d_smr <- d_smr |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

@@

```{r}
d_dpvar1 <- d_migr |>
  select(migr, 
         cog_dif, cog3pl, w2cog3pl, ttl_dif, w1ttl_100, w2ttl_100) |>
  set_variable_labels(
    migr = 'Parental migration',
    cog3pl ='Wave 1 score',
    w2cog3pl = 'Wave 2 score',
    w1ttl_100='Wave 1 score',
    w2ttl_100 = 'Wave 2 score',
    cog_dif = 'Cognitive test score difference',
    ttl_dif = 'Academic exam score difference'
  )
```

```{r}
tab_dpvar <- 
  st(
  data = d_dpvar1,
  summ = c('mean(x)', 'sd(x)'),
  digits = 2, 
  group = 'migr',
  group.test = list(
    star.cutoffs = c(0.001, 0.01, 0.05),
    format = 'p={pval}{stars}'),
  labels = T,
  out = 'return') 
tab_dpvar <- tab_dpvar[-c(1),]
tab_dpvar[tab_dpvar == 'p=&lt0.001***'] <- 'p<0.001***'
tab_dpvar 
```

```{}
d_dpvar <- as.data.frame(d_dpvar)
table_dependent_variable <- datasummary(
  All(d_dpvar) ~ Mean + SD + Min + Max,
  data = d_dpvar,
  output = 'markdown'
  ) 
table_dependent_variable
```

```{r}
d_idpvar <- d_migr |> 
  select(migr, migr_mo_only, migr_fa_only, migr_both) |> 
  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) |> 
  mutate(`Parental Migration Type` = 0) 
d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents At Home'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother Migrated'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father Migrated'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
d_idpvar <- d_idpvar |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

@@

```{r}
d_ctvar_dit <- d_migr |>
  select(migr, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet) |> 
  mutate_all(as_factor)
```

```{r}
d_ctvar_cnt <- d_migr |>
  select(migr, child.age, child.health.self.rated, child.educational.aspiration, 
  parent.educational.level, parent.expectation.on.child, 
  home.extracurricular.book, home.economic.resource)
```

```{r}
d_ctvar <- d_ctvar |> 
  add_value_labels(
    parent.educational.level = c(
     'Primary school and below' = 1,
     'Junior high school' = 2 ,
     'Senior high school' = 3,
     'Associate college' = 4,
     'University' = 5,
     'Postgraduate' = 6),
    child.educational.aspiration = c(
     'Junior high school' = 1 ,
     'Senior high school' = 2,
     'Associate college' = 3,
     'University' = 4,
     'Postgraduate' = 5),
    child.educational.aspiration = c(
     'Junior high school' = 1 ,
     'Senior high school' = 2,
     'Associate college' = 3,
     'University' = 4,
     'Postgraduate' = 5), 
    parent.expectation.on.child = c(
     'Junior high school' = 1 ,
     'Senior high school' = 2,
     'Associate college' = 3,
     'University' = 4,
     'Postgraduate' = 5),
    home.economic.resource = c(
      'Very poor' = 1,
      'Somewhat poor' = 2,
      'Moderate' = 3,
      'Somewhat rich' = 4,
      'Very rich' = 5),
    child.health.self.rated = c(
      'Very poor' = 1,
      'Somewhat poor' = 2,
      'Moderate' = 3,
      'Good' = 4,
      'Very good' = 5),
    home.extracurricular.book = c(
      'Very few' = 1,
      'Not many' = 2,
      'Some' = 3,
      'Quite a few' = 4,
      'A great number' = 5),
    )
```

```{}
test.table <- d_ctvar |>
  tbl_summary(
    by = migr,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    ) 
```

```{r}
test_table <- datasummary_balance(
  ~migr,
  data = d_ctvar,
  output = 'markdown'
)
test_table
```

```{r}
tab_ctvar_dit <- 
  st(
  data = d_ctvar_dit,
  digits = 2,
  group = 'migr',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = "return"
  )
tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
tab_ctvar_dit[tab_ctvar_dit == 3452|tab_ctvar_dit == 636] <- ''
```

```{}
tab_ctvar_cnt <- d_ctvar_cnt |> st(
  digits = 2, 
  summ = c('mean(x)', 'sd(x)'),
  group = 'migr',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = "return")
tab_ctvar_cnt <- tab_ctvar_cnt[-c(1),]
```

```{}
table_control_variable <- datasummary_skim(
  data = d_ctvar,
  type = 'categorical',
  output = 'markdown'
)
table_control_variable
```

```{r}
table_sum <- d_ctvar |> st(
  group = 'migr',
  summ = c('mean(x)', 'sd(x)'),
  digits = 2, 
  out = 'return')
table_sum
```

@@

```{r}
set.seed(1)
fig_cog <- d_smr |>
  ggplot(aes(x=`Parental Migration`, y=cog_dif, fill=`Parental Migration`)) + 
    geom_violin()+
    xlab('Parental Migration') +
    theme(legend.position="none") +
    ylab('Cognitive Test Score Difference') +
    stat_summary(
      fun = "mean",
      geom = "crossbar", 
      size = 0.4,
      width = 0.5) +
  scale_fill_manual(values = alpha(c("green", "red"), .3))
fig_cog
```

```{r}
set.seed(1)
fig_ttl <-  d_smr |>
  ggplot(aes(x=`Parental Migration`, y=ttl_dif, fill=`Parental Migration`)) + 
    geom_violin()+
    xlab('Parental Migration') +
    theme(legend.position="none") +
    ylab('Academic Exam Score Difference') +
    stat_summary(
      fun = "mean",
      geom = "crossbar", 
      size = 0.4,
      width = 0.5) +
  scale_fill_manual(values = alpha(c("green", "red"), .3))
fig_ttl
```
